---
title: "Programming Assignment 3"
author: "Kevin Ismantara"
date: '2018-11-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("stats")
library("randomForest")
library("pROC")
library("ggplot2")
library("caret")
```

Import data: 
```{r}
newTrainData <- read.csv(file="./Titanic.Train.csv", header=TRUE, sep=",", na.strings=c("","NA"))
newTestData <- read.csv(file="./Titanic.Test.csv", header=TRUE, sep=",", na.strings=c("","NA"))
newTrainData$survived <- factor(newTrainData$survived)
newTestData$survived <- factor(newTestData$survived)
```

Task 1: Learn & Plot ROC curve of random forest
```{r}
forestLearn <- randomForest(survived ~., data=newTrainData, ntree=100)
prediction <- predict(forestLearn, newTestData, type="class")
correct <- newTestData$survived 
confusionMatrix <- table(correct, prediction)
accuracyScore <- mean(correct == prediction)
rocCurve <- roc(newTrainData$survived, forestLearn$votes[,2])
plot(rocCurve)
aucForest <- auc(rocCurve)
print(paste0("Area Under Curve: ", aucForest))
```

Task 2: Analyze the importance of the different attributes
```{r}
importanceOfAttributes <- importance(forestLearn)
importancePlot <- varImpPlot(forestLearn)
```
Based on the plot above, the top 3 most important attributes when determining survival are in the following order of significance: Sex, Age, Fare

Task 3: Learn Regression Model
```{r}
library("glmnet")
library("e1071")
newTrain <- newTrainData[c("survived", "pclass", "sex", "age", "sibsp",
"parch", "fare")]

newTest <- newTestData[c("survived", "pclass", "sex", "age", "sibsp","parch", 
"fare")]
regressionModel <- train(survived ~., data=newTrain, method="glmnet")
summary(regressionModel)
```

Task 4: Predict using regression model, plot confusion matrix, accuracy
```{r}
library("ROCR")
regressionPrediction <- predict(regressionModel, newTest, probability=TRUE)
numericRegressionPrediction <- prediction(as.numeric(regressionPrediction), as.numeric(newTest$survived))
rocRegression <- performance(numericRegressionPrediction, measure = "tpr", x.measure="fpr")
plot(rocRegression)
performance(numericRegressionPrediction, measure="auc")

correctRegression <- newTest$survived 
confusionMatrixRegression <- table(correctRegression, regressionPrediction)
print(confusionMatrixRegression)
correct <- newTest$survived 

accuracyScore <- mean(correct == regressionPrediction)
print(paste0("Accuracy score of logistic regression: ", accuracyScore))
```

Task 5: SVM
```{r}
linearTune <- tune.svm(survived ~., data=newTrain, kernel="linear", cost = 3^(0:2), gamma=3^(-2:0))
summary(linearTune)
linearTuneBestTrain <- svm(survived ~., data=newTrain, kernel="linear", cost = 3, gamma=0.33)
linearTuneBestTest <- svm(survived ~., data=newTest, kernel="linear", cost = 3, gamma=0.33)
                      
radialTune <- tune.svm(survived ~., data=newTrain, kernel="radial", cost = 3^(0:2), gamma=3^(-2:0))
summary(radialTune)
radialTuneBestTrain <- svm(survived ~., data=newTrain, kernel="radial", cost = 1, gamma=0.11)
radialTuneBestTest <- svm(survived ~., data=newTest, kernel="radial", cost = 1, gamma=0.11)
```

Task 6: Predict SVM
```{r}
library("ROCR")
linearSVMPredict <- predict(linearTuneBestTrain, newTest)
numericLinearSVMPrediction <- prediction(as.numeric(linearSVMPredict), as.numeric(newTest$survived))
rocLinear <- performance(numericLinearSVMPrediction, measure = "tpr", x.measure="fpr")
plot(rocLinear)
performance(numericLinearSVMPrediction, measure="auc")

correctRegression <- newTest$survived 
confusionMatrixLinearSVM <- table(correctRegression, linearSVMPredict)
print(confusionMatrixLinearSVM)
correct <- newTest$survived 

accuracyScoreLinearSVM <- mean(correct == linearSVMPredict)
print(paste0("Accuracy score of SVM with linear kernel: ", accuracyScoreLinearSVM))


radialSVMPredict <- predict(radialTuneBestTrain, newTest)
numericRadialSVMPrediction <- prediction(as.numeric(radialSVMPredict), as.numeric(newTest$survived))
rocRadial <- performance(numericRadialSVMPrediction, measure = "tpr", x.measure="fpr")
plot(rocRadial)
performance(numericRadialSVMPrediction, measure="auc")

correctRegression <- newTest$survived 
confusionMatrixRadialSVM <- table(correctRegression, radialSVMPredict)
print(confusionMatrixRadialSVM)
correct <- newTest$survived 

accuracyScoreRadialSVM <- mean(correct == radialSVMPredict)
print(paste0("Accuracy score of SVM with radial kernel: ", accuracyScoreRadialSVM))
```




