---
title: "Programming Assignment 4"
author: "Kevin Ismantara"
date: '2018-12-05'
output: html_document
---

```{r setup, include=FALSE}
library("arules")
```

Question 1:
```{r}
data <- data(Groceries)
itemsPerTransaction <- summary(Groceries)@lengths
plot(itemsPerTransaction, xlab="Number of Items per Transaction", ylab="Total Number of Transactions", main="Histogram")
```
I can see that there are more people who make frequent trips to the grocery 
<br/>
store, while spending less per trip. This leads me to believe that this grocery
<br/>
store is more of a convencience store such as 7-11, or a streetside grocery store
<br/>
where people only buy a few items per trip as opposed to larger supermarkets such as 
<br/>
T&T or Superstore. 

Question 2:
```{r}
frequentItemSet1 <- apriori(Groceries, parameter=list(supp=0.001,target="frequent"))
frequentItemSet2 <- apriori(Groceries, parameter=list(supp=0.01,target="frequent"))
frequentItemSet1 #support: 0.001 - 13492 itemsets
frequentItemSet2 #support: 0.01 - 333 itemsets
closedFrequentItemSet1 <- apriori(Groceries, parameter = list(supp=0.001, target="closed"))
closedFrequentItemSet2 <- apriori(Groceries, parameter = list(supp=0.01, target="closed"))
closedFrequentItemSet1  #support: 0.001 - 13464 itemsets
closedFrequentItemSet2  #support: 0.01 - 333 itemsets
maximalFrequentItemSet1 <- apriori(Groceries, parameter = list(supp=0.001, target="maximal"))
maximalFrequentItemSet2 <- apriori(Groceries, parameter = list(supp=0.01, target="maximal"))
maximalFrequentItemSet1 # support: 0.001 - 7794 itemsets
maximalFrequentItemSet2 # support: 0.01 - 243 itemsets
```

Question 3:
```{r}
sortedFrequentItemSet <- sort(frequentItemSet1)
inspect(sortedFrequentItemSet[1:10,])
```

Question 4: 
Based on the histogram on question 1, we can see that most of transactions that happen in the grocery store 
<br/>
are customers who only buy 1 item. With this information, we can expect that there would be a low frequent itemset. 
<br/>
This would also explain why the frequent itemsets, closed frequent itemsets, and maximal frequent itemsets
<br/>
are very similar to one another.

Question 5: 
```{r}
associationRules <- apriori(Groceries, parameter = list(supp=0.01, conf=0.9 ,target="rules"))
associationRules1 <- apriori(Groceries, parameter = list(supp=0.01, conf=0.45 ,target="rules"))
associationRules2 <- apriori(Groceries, parameter = list(supp=0.01, conf=0.5 ,target="rules"))
associationRules3 <- apriori(Groceries, parameter = list(supp=0.01, conf=0.55 ,target="rules"))
associationRules4 <- apriori(Groceries, parameter = list(supp=0.01, conf=0.51 ,target="rules"))
associationRules5 <- apriori(Groceries, parameter = list(supp=0.01, conf=0.52 ,target="rules"))
associationRules # 0 rules
associationRules1 # 31 rules
associationRules2 # 15 rules
associationRules3 # 7 rules
associationRules4 # 12 rules
associationRules5 # 9 rules
```
With a minimum confidence of 0.9, we get 0 association rules. To get at least more than 10 rules, we need to lower
the confidence to 0.51 to get 12 rules.

Question 6: 
```{r}
wholeMilkOnRHS <- subset(associationRules2, subset = rhs %pin% "whole milk")
inspect(head(wholeMilkOnRHS, n=11, by="lift"))
```

Question 7: 
<br/>
From task 6, we can see that the top rules are as follows along with its lift: 
<br/>
1. (curd, yogurt) => (whole milk)  - 2.279125 
<br/>
2. (other vegetables, butter) => (whole milk) - 2.244885 
<br/>
3. (tropical fruit, root vegetables) => (whole milk) - 2.230969
<br/>

It is not surprisng to see that when a person buys curd and yogurt, they tend to buy milk as well.
<br/>
Part of the reason is that Milk is a rather common breakfast item that can be used in versatile ways.