---
title: "Programming Assignment 2"
author: "Kevin Ismantara"
date: '2018-10-24'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("stats")
library("cluster")
library("clusteval")
library("BBmisc")
library("ggplot2")
library("tree")
```

## R Markdown

# Task 1: Load & Split data
```{r}
TitanicData <- read.csv(file="./titanic3.csv", header=TRUE, sep=",", na.strings=c("","NA"))
set.seed(1)
dt = sort(sample(nrow(TitanicData), nrow(TitanicData)*0.8))
trainData <- TitanicData[dt,]
testData <- TitanicData[-dt,]
```

# Task 2: Number of missing values
```{r}
colSums(is.na(trainData))
colSums(is.na(testData))
```

# Task 3: Attributes for survival prediction
Use attributes: Pclass, survived, sex, age, sibsp, parch, fare. 
The other attributes do not play a factor in a person's survival. 

# Task 4:
```{r}
trainData$age[is.na(trainData$age)] <- mean(trainData$age, na.rm=TRUE)
testData$age[is.na(testData$age)] <- mean(testData$age, na.rm=TRUE)

trainData$cabin <- NULL
trainData$boat <- NULL
trainData$body <- NULL
trainData$home.dest <- NULL
testData$cabin <- NULL
testData$boat <- NULL
testData$body <- NULL
testData$home.dest <- NULL

trainData <- trainData[!is.na(trainData$name),]
trainData <- trainData[!is.na(trainData$embarked),]
trainData <- trainData[!is.na(trainData$fare),]

trainData$survived <- factor(trainData$survived)
testData$survived <- factor(testData$survived)

colSums(is.na(trainData))
colSums(is.na(testData))
```
1. For the age column: replace N/A with average age
2. Delete columns Cabin, boat, body, and home.dest
3. Delete the row with missing name, embarked, or fare from training data. Test data has no empty rows

# Task 5
```{r}
trainData$ticket <- NULL
trainData$name <- NULL

newTrainData <- trainData[c("survived", "pclass", "sex", "age", "sibsp",
                            "parch", "fare", "embarked")]

newTestData <- testData[c("survived", "pclass", "sex", "age", "sibsp","parch", 
                          "fare", "embarked")]

# Plot decision tree
decisionTree <- tree(formula = survived ~. , data= newTrainData)
plot(decisionTree)
text(decisionTree, all=TRUE)
summary(decisionTree)


prediciton <- predict(decisionTree, newTestData, type="class")
correct <- testData$survived 
confusionMatrix <- table(correct, prediciton)
accuracyScore <- mean(correct == prediciton)
```
Size of tree: 7
Accuracy score: 77.5%

# Task 6
The top 3 most important attributes from most to least important are: pclass, sibsp, fare
pclass is the most important attribute is because from the decision tree, we can see that 
a decision whether or not a passenger survives is based on the pclass, whether or not they are 
male or female. Pclass can affect the position of the cabins (higher or lower floor). This is 
a huge factor when trying to evacuate a large ship. 

Siblings also play an important factor when predicting survival, as seen from the decision tree, 
it determines whether or not a passenger survives if they have less than 3 siblings or not. This is
partly due to the fact that family members will not leave one another in the case of an emergency 
and might be too late for them if they take too long to find one another

Last but not least, the fare class also determines whether or not a passenger survives. This might be due 
to the fact that passengers who are less wealthy (pay less fare) tend to have better survival skills then 
passengers who are wealthy. 

Before looking at the decision tree, I thought the greatest factor that would affect survival would be sex, age, 
and number of siblings, however, after analyzing the decision tree, I realize that this is not true. Not only that,
it turns out the attributes that I assumed to be the greatest factor turns out to be one of the least deciding factors.

# Task 7
```{r}
crossValidationTree <-cv.tree(decisionTree)
bestIndex <- which(crossValidationTree$dev == min(crossValidationTree$dev))
optimizedTree <- crossValidationTree$size[bestIndex]

prunedTree <- prune.misclass(decisionTree, best = optimizedTree)
plot(prunedTree)
text(decisionTree, all=TRUE)
summary(prunedTree)
```
Size of pruned tree: 7